Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-12 hotstorage13/abs.tex
resource...

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
hosting  reliability; however, it  takes significant 
memory resource to perform data duplication in order to remove
excessive redundancy among snapshots.
This paper presents a low-cost deduplication solution scalable for a large number 
of virtual machines.  The key idea is to separate duplicate detection from 
the actual storage backup instead of using inline deduplication, and partition
global index and  detection requests among machines using  fingerprint values.
Then each machine conducts duplicate detection partition by partition independently with a minimal memory usage.
%in parallel among all machines and  each machine full duplication detection is 
Another optimization is to allocate and control
buffer space for exchanging  detection requests and duplicate summary among machines.
%The memory requirement and disk usage for the proposed solution is very small while the overall thoughput
%and backup process timing is not compromised. 
Our evaluation shows that  the proposed multi-stage scheme 
uses a very small amount of system resources while delivering a satisfactory backup throughput.
%in a large cloud setting.
%which only reqiires a very small amount of memory and CPU resource.  
%Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
%a  small  amount of cloud resources.

>>>>

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
hosting  reliability; however, it  takes significant 
memory resource to perform data duplication in order to remove
excessive redundancy among snapshots.
This paper presents a low-cost deduplication solution scalable for a large number 
of virtual machines.  The key idea is to separate duplicate detection from 
the actual storage backup instead of using inline deduplication, and partition
global index and  detection requests among machines using  fingerprint values.
Then each machine conducts duplicate detection partition by partition independently with a minimal memory usage.
%in parallel among all machines and  each machine full duplication detection is 
Another optimization is to allocate and control
buffer space for exchanging  detection requests and duplicate summary among machines.
%The memory requirement and disk usage for the proposed solution is very small while the overall thoughput
%and backup process timing is not compromised. 
Our evaluation shows that  the proposed multi-stage scheme 
uses a small or modest amount of system resources while delivering a satisfactory backup throughput.
%in a large cloud setting.
%which only reqiires a very small amount of memory and CPU resource.  
%Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
%a  small  amount of cloud resources.

### 2013-03-12 hotstorage13/intro.tex
fix typos
resource...

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host
%tens of thousands of  virtual machines(VM) created for various active users.
Periodic  archiving of virtual machine (VM) snaps is important 
for long-term data  retention and fault recovery in case of machine failures.  
For example, daily backup of VM images  is conducted automatically 
at Alibaba which provides the largest public cloud service in China.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
identifies redundant content duplicates among snapshots.  On the other hand, performing
deduplication adds significant  memory cost for comparison of content fingerprints. 
Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
Cloud providers often wish that the backup service only consumes  the minimal resource usage without 
impacting any existing cloud service.  Another challenge for backup with deduplication is that deletion 
of old snapshot competes computing resource also. That is because data dependence created 
by duplicate relationship among snapshots  adds processing complexity.
% especially when  VMs can migrate around in the cloud.

Among the three factors - time, cost and de-deduplication efficiency, one of them has to be compromised for the other two. For instance, if we were building a deduplication system that has a high rate of duplication detection and has a very fast response time, 
it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio
and  the sufficient deduplication  throughput for dealing with a large number of VM images. 
% This business model partially  resembles that of Amazon Glacier.

>>>>

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host
%tens of thousands of  virtual machines(VM) created for various active users.
Periodic  archiving of virtual machine (VM) snaps is important 
for long-term data  retention and fault recovery in case of machine failures.  
For example, daily backup of VM images  is conducted automatically 
at Alibaba which provides the largest public cloud service in China.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
identifies redundant content duplicates among snapshots.  On the other hand, performing
deduplication adds significant  memory cost for comparison of content fingerprints. 
Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently. 
Cloud providers often wish that the backup service only consumes  a small or modest resource usage 
with a minimal impact to the existing cloud services.  Another challenge for backup with deduplication is that deletion 
of old snapshot competes computing resource also. That is because data dependence created 
by duplicate relationship among snapshots  adds processing complexity.
% especially when  VMs can migrate around in the cloud.

Among the three factors - time, cost and deduplication efficiency, one of them has to be compromised for the other two. For instance, if we were building a deduplication system that has a high rate of duplication detection and has a very fast response time, 
it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
Our objective is to lower the cost incurred while sustaining the highest de-duplication ratio
and  a sufficient throughput in dealing with a large number of VM images. 
% This business model partially  resembles that of Amazon Glacier.
